---
title: "Weather & Fatality Rates"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


The following packages were loaded into RStudio to for data wrangling and to reproduce this report:

library(readr)
library(foreign) 
library(rvest) 
library(knitr) 
library(dplyr)
library(openxlsx)
library(magrittr)
library(tidyr)
library(glue)

```{r, echo = TRUE, warning = FALSE, results = FALSE}

library(readr)
library(foreign) 
library(rvest) 
library(knitr) 
library(dplyr)
library(openxlsx)
library(magrittr)
library(tidyr)
library(glue)   
```


A data set was sourced from 'Our World in Data' website and read into the RStudio environment using the 'read.csv'.  

```{r}
fatalityrates1 <- read.csv("fatality-rates-us-due-to-weather-events1.csv")
```


The data used for this report named "Mortality Rates in the US Due to Weather Events" was sourced from Our World In Data which is an open source data website (https://ourworldindata.org/grapher/fatality-rates-in-the-us-due-to-weather-events?country=~USA).

The data was presented as a visualization on the website which can be seen below. This data is also presented in table form which was downloaded for the purpose of this project. :

<iframe src="https://ourworldindata.org/grapher/fatality-rates-in-the-us-due-to-weather-events?country=~USA" loading="lazy" style="width: 100%; height: 600px; border: 0px none;"></iframe>


The data comprises of multiple weather events and their associated mortality rate per million individuals measured over a century on a yearly basis. The variables in this dataset can be seen in the head of the dataset below.

The data was inspected using the view(), head(), tail() and str() functions.

```{r, echo = TRUE, warning = FALSE}
View(fatalityrates1) 
```

```{r, echo = TRUE, warning = FALSE}
head(fatalityrates1)
```

```{r, echo = TRUE, warning = FALSE}
tail(fatalityrates1)
```

```{r, echo = TRUE, warning = FALSE}
str(fatalityrates1)
```

Once the data type of each variable was established, each variable was transformed into the correct data type to enable further data manipulation.
This was done using the "<- as.factor" function.

```{r, echo = TRUE, warning = FALSE}
fatalityrates1$YearFac <- as.factor(fatalityrates1$Year)
fatalityrates1$CodeFac <- as.factor(fatalityrates1$Code)
fatalityrates1$EntityFac <- as.factor(fatalityrates1$Entity)
```

The variables were rearranged for ease of analysis using the "arrange(desc())" function.

```{r, echo = TRUE, warning = FALSE}
fatalityrates1 %<>%
  arrange(desc(Year))
```

A new data frame "fatalityratesnew" was created with the newly converted data types taking only the first 20 rows using the "[]" subset function. The reason for this sub selection was because the large dataset spanning across 115 years contained mostly null variables for majority of the different weather events prior to 1995 which did not make for interesting comparison. It is also not useful to compare mortality rates across such a broad time span as there may be confounding for medical care and treatments that wer available across the century. 

Column names were assigned to the dataset using "colnames()" and the structure was re-evaluated using "str()".

```{r, echo = TRUE, warning = FALSE}
fatalityratesnew <- fatalityrates1[1:20,c("EntityFac", "YearFac", "Wind", "Rip.Current", "Winter", "Cold","Heat","Hurricane","Tornado", "Flood", "Lightning")]
colnames(fatalityratesnew)<- c("Entity","Year", "Wind", "RipOrCurrent", "Winter", "Cold","Heat","Hurricane","Tornado", "Flood", "Lightning")
str(fatalityratesnew)
```

The data was in wide format in that each variable of weather event was in its own column instead of being listed down the rows as a variable type (Wickham, 2014).
The data was pivoted into long format and the new variable which was created was transformed from the character to a factor. The "df%<>%pivot_longer(cols=c())" was used.

```{r, echo = TRUE, warning = FALSE}

fatalityratesnew %<>%
  pivot_longer(cols=c("Wind", "RipOrCurrent", "Winter", "Cold","Heat","Hurricane","Tornado", "Flood", "Lightning"), names_to="Type", values_to="RatePerMillion")
fatalityratesnew$Type <- as.factor(fatalityratesnew$Type)
str(fatalityratesnew)

```

There were two categorical variables which were looked at for summary statistics and grouped together by the numeric variable of mortality rate per million.
Firstly the mean mortality rates were compared year by year using the "group_by()" function and the "summarise()" function. 


```{r, echo = TRUE, warning = FALSE}
fatalityratesnew %>% 
  group_by(Year) %>% 
  summarise(mean_RatePerMillion = mean(RatePerMillion, na.rm = TRUE))


```

Secondly, a full summary statistics set was ran for the type of weather event against the mortality rate per million. 

```{r, echo = TRUE, warning = FALSE}
fatalityratesnew %>% 
  group_by(Type) %>% 
  summarise(Min_RatePerMillion = min(RatePerMillion, na.rm = TRUE), 
            Q1_RatePerMillion = quantile(RatePerMillion, probs = 0.25, na.rm = TRUE), 
            Median_RatePerMillion = median(RatePerMillion, na.rm = TRUE), 
            Q3_RatePerMillion = quantile(RatePerMillion, probs = 0.75, na.rm = TRUE), 
            Max_RatePerMillion = max(RatePerMillion, na.rm = TRUE), 
            Mean_RatePerMillion = mean(RatePerMillion, na.rm = TRUE), 
            SD_RatePerMillion = sd(RatePerMillion, na.rm = TRUE), 
            Missing_RatePerMillion = sum(is.na(RatePerMillion)), 
            n = n())

```

A list of the numbers 1 to 9 was created to represent each type of weather event. These were created into a dataframe with the corresponding weather event listed and named using the "newdf <- data.frame" function. 

```{r, echo = TRUE, warning = FALSE}
newdf <- data.frame (TypeNumber = 1:9,
                   Type = c("Wind", "RipOrCurrent", "Winter", "Cold", "Heat", "Hurricane", "Tornado", "Flood", "Lightning"))
newdf

```

The above list was then joint to the transformed data frame using a left join in order to assign each number to its corresponding weather event type using the "<- left_join()" function. 

```{r, echo = TRUE, warning = FALSE}
JoinedFatality <- left_join(fatalityratesnew, newdf, by = c("Type"))

JoinedFatality
```

A subset was created from the new data frame using the first 10 rows of the dataset across all the variables using the "[row,cols()]" subset function.

```{r, echo = TRUE, warning = FALSE}

fatalitysubset1 <- JoinedFatality[1:10,c("Entity", "Year", "Type", "RatePerMillion", "TypeNumber")]

fatalitysubset1

```

The subset was then converted into a matrix using the "<- as.matrix()". The structure of the matrix was a character. This is because the subset from the previous dataset contained both numeric and factor variable so RStudio will automatically label these both to character data type. 

```{r, echo = TRUE, warning = FALSE}
fatalitymatrix <- as.matrix(fatalitysubset1)

str(fatalitymatrix)
```

The data frame was again subsetted using the [] function, this time only including the first and last variable in the data set. It was then saved as an R object file.

```{r, echo = TRUE, warning = FALSE}
fatalitysubset2 <- JoinedFatality[c(1,180), c(1,5)]

fatalitysubset2

```

A new data frame was created using the two variables named "Temperature" and "Degrees", one a ordinal variable and one an integer variable respectively. 

```{r, echo = TRUE, warning = FALSE}
holidaydf <- data.frame(Temperature = c("Freezing", "Cool", "Mild", "Warm", "Hot"),
                        Degrees= c(0, 10, 20, 30, 40))


str(holidaydf)
```
Another numeric vector was created and "cbind()" function was used to add this vector to the "holidaydf" 

```{r, echo = TRUE, warning = FALSE}
Ranking <- factor(c(1:5))
                    
holidaydf2  <-cbind(holidaydf, Ranking)                

holidaydf2                   
```

Another data frame was created with the "Degrees" common variable to the previous dataframe but with another variable included called "Activity".

```{r, echo = TRUE, warning = FALSE}
holidaydf3 <- data.frame(Degrees  = c(0, 10, 20, 30, 40),
                   Activity = c("Skiing", "Hiking", "Tennis", "Walking", "Swimming"))
holidaydf3
```
The above data frame was joined to a new dataframe named "HolidayJoined" using a left join to align the "Activity" variable with its respective variable "Degrees" in the previous dataset. 
```{r, echo = TRUE, warning = FALSE}
HolidayJoined <- left_join(holidaydf2, holidaydf3, by = c("Degrees"))

HolidayJoined

```


## References:

Wickham, H 2014, 'Tidy Data (Links to an external site.)', Journal of Statistical Software, vol. 59, no.10, pp. 1-23.




<br>
<br>
